---
title: "PGx analysis"
output: html_notebook
---
```{r}
library("ggpubr")
```

reading data
```{r}
library(readxl)
responses <- read_excel("Genetic Counselors Knowledge of Pharmacogenomics.xlsx", 
     skip = 2)

```

counting responses to each question
```{r}
responses$q2 <- as.integer(responses$question_2=="CYP2C19 *1")
responses$q3 <- as.integer(responses$question_3=="Codeine")
responses$q4 <- as.integer(responses$question_4=="They are an ultra-metabolizer")
responses$q5 <- as.integer(responses$question_5=="Increased enzyme activity, causing someone to experience symptoms of a higher dose of the drug than they were given")
responses$q6 <- as.integer(responses$question_6=="False")
responses$q7 <- as.integer(responses$question_7!="Never")
responses$q8 <- as.integer((responses$question_8=="Agree" | responses$question_8=="Strongly agree"))
responses$q9 <- as.integer((responses$question_9=="Agree" | responses$question_9=="Strongly agree"))
responses$q10 <- as.integer(as.factor(responses$question_10))
responses$q13 <- as.integer(as.factor(responses$question_13))
```


converting NA responses to a zero value
```{r}
responses[is.na(responses)] <- 0
```

summation of correct answers in questions 2 through 6
```{r}
responses$knowledgesum <- responses$q2+responses$q3+responses$q4+responses$q5+responses$q6
```

number of participants that have greater than 2 questions correct within questions 2 through 6
```{r}
sum(responses$knowledgesum>2)
```

summation of correct answers in questions 2 through 9
```{r}
responses$totalsum <- responses$q2+responses$q3+responses$q4+responses$q5+responses$q6+responses$q7+responses$q8+responses$q9
```

number of participants that have greater than 4 questions correct within questions 2 through 9
```{r}
sum(responses$totalsum>4)
```

correlation test between knowledge and relevancy score and when someone graduated

```{r}
cor.test(responses$q10, responses$totalsum, method = "pearson")
```

graph of above correlation test

```{r}
ggscatter(responses, x = "q10", y = "totalsum", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "gradyears", ylab = "score")
```

correlation test between agreeing with pharmacogenomic relevancy and what type of position the GC works in
```{r}
cor.test(responses$q13, responses$q9, method = "pearson")
```


```{r}
ggscatter(responses, x = "q13", y = "q9", 
          conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "typeofjob", ylab = "relevancy")
```


table so you can correlate the 1-5 above with category job type from survey
```{r}
table(as.factor(responses$question_13))
table(as.integer(as.factor(responses$question_13))-1)
```

Group/count of job type and X is if pharmacogenomics is relevant or not
```{r}
res <- aggregate(responses$q9, by=list(responses$question_13, responses$q9), FUN=length)
res[res$Group.2 == 1,]
```


correlation test between agreeing with pharmacogenomic relevancy and years since graduation
```{r}
cor.test(responses$q10, responses$q9, method = "pearson")
```


```{r}
ggscatter(responses, x = "q10", y = "q9", 
          conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "typeofjob", ylab = "relevancy")
```


table so you can correlate the 1 or 2 above to which answer in survey
```{r}
table(as.factor(responses$question_10))
table(as.integer(as.factor(responses$question_10)))
```

Group/count of job type and X is if pharmacogenomics is relevant or not
```{r}
res <- aggregate(responses$q9, by=list(responses$question_10, responses$q9), FUN=length)
res[res$Group.2 == 1,]
```


















