---
title: "PGx analysis"
output: html_notebook
---
reading data
```{r}
library(readxl)
responses <- read_excel("Genetic Counselors Knowledge of Pharmacogenomics.xlsx", 
     skip = 2)

```

counting responses to each question
```{r}
responses$q2 <- responses$question_2=="CYP2C19 *1"
responses$q3 <- responses$question_3=="Codeine"
responses$q4 <- responses$question_4=="They are an ultra-metabolizer"
responses$q5 <- responses$question_5=="Increased enzyme activity, causing someone to experience symptoms of a higher dose of the drug than they were given"
responses$q6 <- responses$question_6=="False"
responses$q7 <- responses$question_7!="Never"
responses$q8 <- (responses$question_8=="Agree" || responses$question_8=="Strongly agree")
responses$q9 <- (responses$question_9=="Agree" || responses$question_8=="Strongly agree")
responses$q10 <- as.factor(responses$question_10)
```

converting NA responses to a zero value
```{r}
responses[is.na(responses)] <- 0
```

summation of correct answers in questions 2 through 6
```{r}
responses$knowledgesum <- responses$q2+responses$q3+responses$q4+responses$q5+responses$q6
```

number of participants that have greater than 2 questions correct within questions 2 through 6
```{r}
sum(responses$knowledgesum>2)
```

summation of correct answers in questions 2 through 9
```{r}
responses$totalsum <- responses$q2+responses$q3+responses$q4+responses$q5+responses$q6+responses$q7+responses$q8+responses$q9
```

number of participants that have greater than 4 questions correct within questions 2 through 9
```{r}
sum(responses$totalsum>4)
```

anova